Self Regulation Ontology Retest Data: Initial Exploration

### 2017-02-28 SRO_Retest_Analyses.Rmd
cont working on retest exploration

Trying to use `lavaan` first. It's not happy with me.
```{r eval=FALSE}
unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")

@@

Using the `psych` package I get some sort of solution but these are probably not valid given all the warnings.
```{r eval = FALSE}
corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')

@@

```{r eval = FALSE}
print(solution$loadings, sort=T)
```

>>>>

Trying to use `lavaan` first. It's not happy with me.
```{r}
unrotated <- efaUnrotate(rest_subs_test_mngf_z, nf=3, varList=names(rest_subs_test_mngf_z)[-1], estimator="mlr")

@@

Using the `psych` package I get some sort of solution but these are probably not valid given all the warnings.
```{r}
corMat <- rest_subs_test_mngf_z %>% select(-sub_id) %>% cor(.,use = 'complete.obs')

@@

```{r}
print(solution$loadings, sort=T)
```
